Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-16 tsibbletalk.Rmd
i think i'm done. cc @dicook

A group of cohesive observational units measured over time typically form one temporal data set. Ensemble graphics [@unwin_ensemble_2018] that bundle multi-views for a data set together, are essential for exploring and mining many different aspects of temporal data. Adding interactivity, such as linked brushing via common observations and wrapping by time, can accelerate this process.

There are a plenty of R packages, but few

@@

```{r wrap-ped, fig.show = "hold", fig.cap = "The shiny module for wrapping the \\code{pedestrian20} data.", fig.subcap = c("Initial overview state", "1-day state", "7-day state"), fig.ncol = 1}
include_graphics("img/wrap-0.png")
include_graphics("img/wrap-1.png")
include_graphics("img/wrap-7.png")
```

@@

The wrapping procedure involves slicing time indices into seasonal periods of interest and their corresponding time dices. For example, hourly pedestrian data can be decomposed into 24-hour blocks grouped by all respective days, like Figure \ref{fig:wrap-ped-2}. Figure \ref{fig:wrap-ped} suggests that there could be more than one eye-catching slices out of many possible combinations, and thus repeated wrappings can be unwieldy. To visually locate an interesting slice, the \CRANpkg{tsibbletalk} package implements a shiny module, a pair of UI and server functions, to automate this wrapping procedure.

@@

The new shiny module exploits the temporal aspect for a tsibble object. It allows users to slide through relative periods to explore seasonal insights, with slick user experience.

@@

A new shiny module, `tsibbleWrapUI()` and `tsibbleWrapServer()`, provides a lens for exploring temporal aspects for a `tsibble`, in particular seasonal variations.

>>>>

A group of cohesive observational units measured over time typically form one temporal data set. Ensemble graphics [@unwin_ensemble_2018] that bundle multi-views for a data set together, are essential for exploring and mining many different aspects of temporal data. Adding interactivity, such as linked brushing via shared observations and wrapping by time, can accelerate this process.

@@

```{r wrap-ped, fig.show = "hold", fig.cap = "The shiny module for wrapping the \\code{pedestrian20} data.", fig.subcap = c("Initial overview state", "1-day state", "7-day state, anchoring to Monday"), fig.ncol = 1}
include_graphics("img/wrap-0.png")
include_graphics("img/wrap-1.png")
include_graphics("img/wrap-7.png")
```

@@

The wrapping procedure involves slicing time indices into seasonal periods of interest and their corresponding time dices. For example, hourly pedestrian data can be decomposed into 24-hour blocks grouped by all respective days, like Figure \ref{fig:wrap-ped-2}. Figure \ref{fig:wrap-ped} suggests that there could be more than one eye-catching slices out of many possible combinations, and thus repeated wrappings can be unwieldy. To visually locate a salient slice, the \CRANpkg{tsibbletalk} package implements a shiny module, a pair of UI and server functions, to automate this wrapping procedure.

@@

The new shiny module exploits the temporal aspect for a tsibble object, exposed by the `index` attribute. It allows users to slide through relative periods to digest seasonal behaviours, with slick user experience.

@@

A new shiny module, `tsibbleWrapUI()` and `tsibbleWrapServer()`, provides a lens for looking at temporal aspects for a `tsibble`, in particular seasonal or cyclical variations. The slicing and dicing technique efficiently wrap time lines for user-defined plots. The `plotlyProxy()` react method makes it possible to send wrapped data to the server and amend the plot straight way.

### 2020-09-16 tsibbletalk.tex
i think i'm done. cc @dicook

A group of cohesive observational units measured over time typically
form one temporal data set. Ensemble graphics
\citep{unwin_ensemble_2018} that bundle multi-views for a data set
together, are essential for exploring and mining many different aspects
of temporal data. Adding interactivity, such as linked brushing via
common observations and wrapping by time, can accelerate this process.

There are a plenty of R packages, but few

@@

{\centering \subfloat[Initial overview state\label{fig:wrap-ped-1}]{\includegraphics[width=\textwidth]{img/wrap-0} }\newline\subfloat[1-day state\label{fig:wrap-ped-2}]{\includegraphics[width=\textwidth]{img/wrap-1} }\newline\subfloat[7-day state\label{fig:wrap-ped-3}]{\includegraphics[width=\textwidth]{img/wrap-7} }

@@

The new shiny module exploits the temporal aspect for a tsibble object.
It allows users to slide through relative periods to explore seasonal
insights, with slick user experience.

@@

A new shiny module, \texttt{tsibbleWrapUI()} and
\texttt{tsibbleWrapServer()}, provides a lens for exploring temporal
aspects for a \texttt{tsibble}, in particular seasonal variations.

>>>>

A group of cohesive observational units measured over time typically
form one temporal data set. Ensemble graphics
\citep{unwin_ensemble_2018} that bundle multi-views for a data set
together, are essential for exploring and mining many different aspects
of temporal data. Adding interactivity, such as linked brushing via
shared observations and wrapping by time, can accelerate this process.

@@

{\centering \subfloat[Initial overview state\label{fig:wrap-ped-1}]{\includegraphics[width=\textwidth]{img/wrap-0} }\newline\subfloat[1-day state\label{fig:wrap-ped-2}]{\includegraphics[width=\textwidth]{img/wrap-1} }\newline\subfloat[7-day state, anchoring to Monday\label{fig:wrap-ped-3}]{\includegraphics[width=\textwidth]{img/wrap-7} }

@@

The new shiny module exploits the temporal aspect for a tsibble object,
exposed by the \texttt{index} attribute. It allows users to slide
through relative periods to digest seasonal behaviours, with slick user
experience.

@@

A new shiny module, \texttt{tsibbleWrapUI()} and
\texttt{tsibbleWrapServer()}, provides a lens for looking at temporal
aspects for a \texttt{tsibble}, in particular seasonal or cyclical
variations. The slicing and dicing technique efficiently wrap time lines
for user-defined plots. The \texttt{plotlyProxy()} react method makes it
possible to send wrapped data to the server and amend the plot straight
way.
